\sysfull

### 2017-08-12 paper/compiler.tex

\sys provides compiler support for \emph{automatic task generation} that simplifies writing task-based code by automatically translating C code into a task-based executable. Doing so requires identifying program points to use as task boundaries, defining a set of task functions that begin and end at those boundaries, ensuring that all existing control-flow paths are either contained within a task, or are made explicit in inter-task control-flow, and identifying and instrumenting accesses to task-shared variables that need to be protected by \sys at runtime. The \sys compiler, \textcolor{red}{based on LLVM}, first analyzes the control-flow graph (CFG) and, using a rule-based heuristic, determines at which points to place a task boundary. After identifying where to put task boundaries, the \sys compiler transforms the imperative code into tasks, instrumenting protected memory accesses.

>>>>

\sys provides compiler support for \emph{automatic task generation} that simplifies writing task-based code by automatically translating C code into a task-based executable. Doing so requires identifying program points to use as task boundaries, defining a set of task functions that begin and end at those boundaries, ensuring that all existing control-flow paths are either contained within a task, or are made explicit in inter-task control-flow, and identifying and instrumenting accesses to task-shared variables that need to be protected by \sys at runtime. The \sys compiler, based on LLVM, first analyzes the control-flow graph (CFG) and, using a rule-based heuristic, determines at which points to place a task boundary. After identifying where to put task boundaries, the \sys compiler transforms the imperative code into tasks, instrumenting protected memory accesses.
